Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-01-19 Report/convergence_centralized.tex
revision_changes

In this approach, we present an algorithm to solve \eqref{eqn-3} to obtain the transmit precoders in a centralized manner by using the idea of alternating optimization and successive convex approximation. Using \eqref{eq:SINR}, we can reformulate the problem defined in \eqref{eqn-3} as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{CCl}\label{eqn-6}
\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\ \beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
\text{subject to}& \quad &\gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}  |^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}) \IEEEyessubnumber \label{eqn-6.2} \\
  & \quad & \beta_{l,k,n} \geq  \tilde{N}_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
  & \quad & \text{and } \eqref{eqn-4.3}, \IEEEyessubnumber
\end{IEEEeqnarray}
}{\allowdisplaybreaks
\begin{IEEEeqnarray}{CCl}\label{eqn-6}
	\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \vspace{-0.25cm}\\
	\text{subject to} &\quad& \gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}) \IEEEyessubnumber \eqspace \label{eqn-6.2} \\
	&\quad& \beta_{l,k,n} \geq \tilde{N}_0 + \sum_{\mathclap{(j,i) \neq (l,k)}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-6.3} \\
	&\quad& \text{and } \eqref{eqn-4.3}, \IEEEyessubnumber
\end{IEEEeqnarray}
}
where \me{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}^\herm, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector which needs to be identified for the optimal allocation and \me{\tilde{N}_0 = N_0\|\mvec{w}{l,k,n}\|^2} be the effective noise variance. In this formulation, we relaxed the equality constraint in \eqref{eq:SINR} by the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3}. However, this step leads to the same solution without loss of optimality, since the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3} are active for an optimal solution, following the same arguments as those in \cite{tran2012fast}. Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by the optimization variable \me{\beta_{l,k,n}}.

Similar to the \ac{WSRM} problem in \cite{tran2012fast}, the proposed formulation in \eqref{eqn-6} can be shown to be NP-hard even for the single antenna case. The reformulation in \eqref{eqn-6} allows a tractable solution as presented below. First, we note that the constraints \eqref{eqn-4.3} are convex with involved variables. Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}. Towards this end, we resort to the traditional coordinate descent technique by fixing the linear receivers, and finding the optimal transmit beamformers. Recall that the coordinate descent method assumes that the optimization variables belong to disjoint sets and the problem must be convex for a given set of variables while keeping other variables fixed as discussed in \cite{xu2013block}.

By fixing the receivers, the problem now is to find the optimal transmit beamformers for a given set of linear receivers which is still a challenging task. We note that for fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity in \eqref{eqn-6.2}. To arrive at a tractable formulation, we adopt the \ac{SCA} method to handle \eqref{eqn-6.2} by replacing the original non-convex constraint by a series of convex constraints. Note that function \me{f(\tilde{\mbf{u}}_{l,k,n})} in \eqref{eqn-6.2} is convex for fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}. According to the \ac{SCA} method, we relax \eqref{eqn-6.2} to a convex constraint in each iteration of the iterative procedure. Since \me{f(\tilde{\mbf{u}}_{l,k,n})} is convex, a concave approximation of \eqref{eqn-6.2} can be easily found by considering the first order approximation of \me{f(\tilde{\mbf{u}}_{l,k,n})} around the current operation point. For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
\begin{subeqnarray} \label{eqn-wsrm-expr}
p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \\
q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}
\end{subeqnarray}
and hence \me{f(\tilde{\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables. In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier}. Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively. Using the first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality constraint as
\iftoggle{single_column}{
\begin{equation}\label{eqn-8}
	2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{equation}
}{
\begin{multline}\label{eqn-8}
2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) \\
+ \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{multline}
}
In summary, for the fixed linear receivers, the \ac{JSFRA} problem to find transmit beamformers is shown by
\begin{IEEEeqnarray}{CCl}\label{eqn-9}
\underset{\substack{\mvec{m}{l,k,n},\\ \gamma_{l,k,n},,\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \vspace{-0.15cm} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  \tilde{N}_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
& \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9.1e}
\end{IEEEeqnarray}

Now, the optimal linear receivers for the fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-3} with respect to \me{\mbf{w}_{l,k,n}} as
\begin{IEEEeqnarray}{CCl}\label{eqn-9--1}
\underset{\substack{\gamma_{l,k,n},\mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
\text{subject to} & \quad & \eqref{eqn-9.1c}, \eqref{eqn-9.1d}, \eqref{eqn-9.1e}, \text{ and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9--1.1b}.
\end{IEEEeqnarray}
Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for the receiver \me{\mvec{w}{l,k,n}} as
\begin{IEEEeqnarray}{rCl}
\mvec{\widetilde{R}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{\widetilde{R}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}, \IEEEyessubnumber \eqspace \label{opt-rx}
\end{IEEEeqnarray}
where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the earlier iteration, upon which the linear relaxation is performed for the nonconvex constraint in \eqref{eqn-9--1}. Note that \eqref{opt-rx} is obtained by iterating over the fixed \me{\mvec{w}{l,k,n}^{(i-1)}} at each \ac{SCA} iteration until convergence or for fixed number of iterations. It can be seen that the optimal receiver expression in \eqref{opt-rx} is in fact a scaled version of the \ac{MMSE} receiver, which is given by
\begin{IEEEeqnarray}{rCl}
\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}. \IEEEyessubnumber \label{eqn-10}
\end{IEEEeqnarray}

The proposed algorithm is referred to as \acl{QM} \ac{JSFRA} scheme with a per \ac{BS} power constraint, and it is outlined in Algorithm \ref{algo-1}. The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached. Instead of initializing \me{\tilde{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with any feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{\tilde{\mbf{u}}_{l,k,n}} in an efficient manner as briefed in Algorithm \ref{algo-1}. For a fixed receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for the predefined iterations, say, \me{J_{\max}} for the optimal transmit precoders \me{\mvec{m}{l,k,n}}. Next, the receive beamformers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}. This procedure is carried out until convergence of the queue deviation or for fixed number of iterations by \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
{\allowdisplaybreaks
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and transmit precoders \me{\tilde{\mbf{M}}_{k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{W}{k,n}} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-8} using \me{\tilde{\mbf{M}}_{k,n}}\;
 \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
 initialize \me{j = 0}\;
 \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
 solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
 update the constraint set \eqref{eqn-8} with \me{\tilde{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
 $j = j + 1$\;
 }
 update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
 $i = i + 1$\;
 }
 \caption{Algorithm of \acs{JSFRA} scheme}
 \label{algo-1}
\end{algorithm}
}

\subsubsection*{Convergence}
In order to prove the convergence of the proposed iterative algorithm, following conditions are to be satisfied \cite{scutari}
\begin{itemize}
	\item convergence of the \ac{SCA} subproblem	
	\item uniqueness of the transmit and the receive beamformers
	\item monotonic convergence of the objective function
\end{itemize}
In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which is majorized by the quadratic-over-linear function in \eqref{eqn-6.2} from below around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}. Since the \ac{SCA} method is adopted in the proposed algorithm, the constraint approximation satisfies the following conditions as in \cite{marks1978technical}
\begin{subeqnarray} \label{sca-req}
	f(\tilde{\mbf{u}}_{l,k,n}) &\leq& \bar{f}(\tilde{\mbf{u}}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	\nabla f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \nabla \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}),
\end{subeqnarray}
where \me{\bar{f}(\mbf{x},\mbf{x}^{(i)})} is the approximate function of \me{f(\mbf{x})} around the point \me{\mbf{x}^{\ast(i)}}. The stationary point of the relaxed convex problem satisfies the \ac{KKT} conditions of the original nonconvex problem, which can be obtained by using conditions in \eqref{sca-req}. It can be seen that the  \ac{SCA} relaxed formulation converges to a local stationary point at each iteration.

@@

>>>>

In order to prove the convergence of the proposed iterative algorithm, following conditions are to be satisfied \cite{scutari}
\begin{itemize}
	\item convergence of the \ac{SCA} subproblem	
	\item uniqueness of the transmit and the receive beamformers
	\item monotonic convergence of the objective function
\end{itemize}
In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which is majorized by the quadratic-over-linear function in \eqref{eqn-6.2} from below around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}. Since the \ac{SCA} method is adopted in the proposed algorithm, the constraint approximation satisfies the following conditions as in \cite{marks1978technical}
\begin{subeqnarray} \label{sca-req}
	f(\tilde{\mbf{u}}_{l,k,n}) &\leq& \bar{f}(\tilde{\mbf{u}}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	\nabla f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \nabla \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}),
\end{subeqnarray}
where \me{\bar{f}(\mbf{x},\mbf{x}^{(i)})} is the approximate function of \me{f(\mbf{x})} around the point \me{\mbf{x}^{\ast(i)}}. The stationary point of the relaxed convex problem satisfies the \ac{KKT} conditions of the original nonconvex problem, which can be obtained by using conditions in \eqref{sca-req}. It can be seen that the  \ac{SCA} relaxed formulation converges to a local stationary point at each iteration.

@@

Following similar approach as in Section \ref{sec-3.2.1}, at each iteration, the \ac{SCA} subproblems converge to a stationary point of the original nonconvex problem. The uniqueness of the precoders are justified if there is no phase ambiguity in the stationary solution. By reorganizing \eqref{eqn-mse-1.3} as
\iftoggle{single_column}{
	\begin{equation}
		\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
	\end{equation}
}{
\begin{multline}
\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} \\ 
+ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
\end{multline}
}
we can see that the ambiguity in the phase rotations for the transmit and the receive beamformers are eliminated by the presence of real component in the \ac{MSE} expression.

At each \ac{SCA} update, the transmit precoders are obtained uniquely by minimizing \eqref{eqn-mse-1} due to the convex nature of the relaxed problem. For a fixed transmit precoders, the \ac{MMSE} receiver improves the objective value \cite{christensen2008weighted,wmmse_shi}, leading to the monotonic convergence of the objective function. At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, and the objective value can either decrease or stays the same after each iteration. Note that the objective function improves at each iteration, whereas the sum rate need not follow the same behavior.

### 2015-01-19 Report/ieee_journal.tex
revision_changes

\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage[ruled]{algorithm2e}
\usepackage[dvipdfmx]{graphicx}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false]{subfig}
\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools,lineno}

@@

@@

\begin{IEEEkeywords}
\ac{MIMO}-\ac{OFDM}, Queue minimizing precoder design, \acs{SCA}, Convex approximation.
\end{IEEEkeywords}

@@

>>>>

\documentclass[10pt,final,onecolumn,letterpaper]{./../Styles/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage[ruled]{algorithm2e}
\usepackage[dvipdfmx]{graphicx}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false]{subfig}
\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools,lineno,verbatim,todonotes,inputenc}

@@

\section{Response to reviewer comments}
\input{review_comments}

@@

\begin{IEEEkeywords}
Convex approximations, \ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, Precoder design, \acs{SCA}, \ac{WSRM}.
\end{IEEEkeywords}

@@

\subsection{Convergence Analysis} \label{sec-3.5}
\input{convergence_centralized}

### 2015-01-19 Report/introduction.tex
revision_changes

In general, the resource allocation problems are formulated by assigning a binary variable to each user indicating the presence or the absence in a particular resource \cite{admission_control}. In contrast to that, we use linear transmit precoders, which are the complex vectors, as a decision variable in determining the presence or the absence of a user on a particular resource. The purpose is two-fold. Firstly, the formulation determines the transmission rate on a certain resource, and, secondly, by making the transmit beamformer of a particular user to be a zero vector, the corresponding user will not be scheduled on a certain resource.

>>>>

In general, the resource allocation problems are formulated by assigning a binary variable to each user indicating the presence or the absence in a particular resource \cite{admission_control}. In contrast to that, we use linear transmit precoders, which are the complex vectors, \review{implicitly} as a decision variable in determining the presence or the absence of a user on a particular resource. The purpose is two-fold. Firstly, the formulation determines the transmission rate on a certain resource, and, secondly, by making the transmit beamformer of a particular user to be a zero vector, the corresponding user will not be scheduled on a certain resource.
